### 2016-05-08 ch01-intro/introduction.tex
Small stuff
Reset acronyms etc. per chapter
Some cleanup, more references input design

\chapter{Introduction}
\def\thisDir{ch01-intro}
\tikzsetfigurename{ch01fig}
\myEpigraph{It's a dangerous business, Frodo, going out your door. You step onto the road, and if you don't keep your feet, there's no knowing where you might be swept off to.}{John Ronald Reuel Tolkien}{The Fellowship of the Ring}

@@

\paragraph{Experiment design}
In the first step, an experiment is constructed to gain insight into the behavior of a system.
For system identification, experiment design is a question of designing input signals that will be applied to the system under test.
Typically, the design consists of constructing a signal such that the obtained model  has a small uncertainty in some sense~\citep{Goodwin1977,Goodwin2006GBO}.
On the one hand, if one has very precise prior information, one could even construct optimal signals~\citep{Gevers2011ExpDesign}.
Typically, the design is very sensitive to the prior knowledge of the system.
This is necessary to focus all the energy in the signal towards exciting the system dynamics as to reduce the uncertainty in the model.
However, when the prior knowledge is incomplete, uncertain or even incorrect, optimal signals can lead to very poor models as they might not excite other dynamics.
An alternative approach is to incorporate the uncertainty of the prior knowledge into the signal design.
This leads to so-called robust optimal experiment design~\citep{Rojas2012,Goodwin2006} that construct signals that optimize the worst-case model uncertainty.
Paradoxically, this means that for robust optimal designs, more prior knowledge, rather than less is required.

@@

\paragraph{Select a model structure}
Once an experiment has been performed, the obtained input-output data is to be processed.
In many cases, the eventual goal of identification is to obtain a parametric model, so the user has to select a model structure and/or complexity based on both his prior knowledge and on the data.
A useful tool to help choose the model structure and/or model orders, is to inspect a nonparametric model of the system.
One such tool is the frequency response function.
For instance, by inspecting a frequency response function, a control engineer can have a rough idea of the system behavior in term of  approximate resonance frequencies, asymptotic slopes, \latin{etc.}
This gives a qualitative view of the minimally required complexity of the model and is hence a useful diagnostic tool.
However, since most parametric estimators enforce very little prior knowledge about the system, noise in the measurements can sometimes be a problem to distinguish the actual system features.
%TODO: peter: also discuss model selection for nonparametric here

>>>>

\chapter{Introduction}
\def\thisDir{ch01-intro}
\tikzsetfigurename{ch01fig}
\glsresetall
\myEpigraph{It's a dangerous business, Frodo, going out your door. You step onto the road, and if you don't keep your feet, there's no knowing where you might be swept off to.}{John Ronald Reuel Tolkien}{The Fellowship of the Ring}

@@

\paragraph{Experiment design}
In the first step, an experiment is constructed to gain insight into the behavior of a system.
For system identification, experiment design is a question of designing input signals that will be applied to the system under test.
Typically, the design consists of constructing a signal such that the obtained model  has a small uncertainty in some sense~\citep{Goodwin1977,Mehra1974,Goodwin2006GBO,Levadi1966}.
On the one hand, if one has very precise prior information, one could even construct optimal signals~\citep{Gagliardi1967,Karlin1966,Gevers2011ExpDesign,Zarrop1979}.
Typically, the design is very sensitive to the prior knowledge of the system.
This is necessary to focus all the energy in the signal towards exciting the system dynamics as to reduce the uncertainty in the model.
However, when the prior knowledge is incomplete, uncertain or even incorrect, optimal signals can lead to very poor models as they might not excite other dynamics.
An alternative approach is to incorporate the uncertainty of the prior knowledge into the signal design.
This leads to so-called robust optimal experiment design~\citep{Rojas2012,Goodwin2006} that construct signals that optimize the worst-case model uncertainty.

@@

\paragraph{Select a model structure}
Once an experiment has been performed, the obtained input-output data is to be processed.
In many cases, the eventual goal of identification is to obtain a parametric model, so the user has to select a model structure and/or complexity based on both his prior knowledge and on the data.
A useful tool to help choose the model structure and/or model orders, is to inspect a nonparametric model of the system.
One such tool is the frequency response function.
For instance, by inspecting a frequency response function, a control engineer can have a rough idea of the system behavior in term of  approximate resonance frequencies, asymptotic slopes, \latin{etc.}
This gives a qualitative view of the minimally required complexity of the model and is hence a useful diagnostic tool.
However, since most parametric estimators enforce very little prior knowledge about the system, noise in the measurements can sometimes be a problem to distinguish the actual system features.

### 2016-05-08 ch03-lrm/nonparametric.tex
Reset acronyms etc. per chapter
Some cleanup, more references input design

\chapter{Non-parametric Modeling}
\def\thisDir{ch03-lrm}
\tikzsetfigurename{ch03fig}
\label{sec:nonparametric}
\myEpigraph{I love deadlines. I like the whooshing sound they make as they fly by.}{Douglas Adams}{}

@@

\subsection{Order Selection}
\label{sec:nparam:orderSelection}
Selecting suitable values of $\nWind$, $\order{B}$, $\order{A}$ and $\order{C}$ obviously affects the quality of the obtained local models.
For local rational models, there are a few insights from parametric system identification that can be retained to make these choices easier.
In particular~\citep{Pintelon2010LPM1}:
\begin{equation}
\order{C} \leq \max\set{\order{B},\order{A}}
\end{equation}
 and from statistical point of view~\citep{Mahata2006}, the degrees of freedom should remain positive such that 
 \begin{equation}
 \nWind \geq \order{B} + \order{A} + \order{C} + 2
 \text{.}
 \end{equation}

@@

\paragraph{Plug-in methods}
In plug-in methods, a goodness-of-fit criterion (e.g. the log-likelihood function $\LogLikelihood$ of the estimated local model $\LocalModel{M}$ given the estimation dataset $\LocalVector{Z}$), is penalized with a term accounting for the complexity of the model~\citep{Burnham2002}.
E.g. a common choice is the \gls{AIC}~\citep{Akaike1974} or the \gls{AICc}~\citep{Hurvich1989}, which are defined as
\begin{align}
\LocalVector{L}_{\AIC} &=
 - 2  \loglikelihood{\LocalModel{M} | \LocalVector{Z}} 
 + 2 \nth
\label{eq:nparam:AIC}\\
\LocalVector{L}_{\AICc} &= 
- 2  \loglikelihood{\LocalModel{M} | \LocalVector{Z}} 
+   \frac{2 \nth\nWind}{\nWind - \nth - 1}
\label{eq:nparam:AICc}
\end{align}
where $\nth$ is the number of  estimated parameters in the model $\LocalModel{M}(\theta)$.
In the context of local modeling, the \gls{AIC} is a poor choice since it relies on asymptotic arguments of the data set, i.e. $\nWind \to \infty$, which is obviously an unwarranted choice in this context.
The best model among a set of $q$ possible models $\Set{\LocalModel{M}^1, \ldots, \LocalModel{M}^q}$ is then
\begin{equation}
  \LocalModel{M}^{\star} \isdef 
  \arg\limits_{\LocalModel{M}} \min 
  \Set{
    \LocalVector{L}_{\mathrm{AIC(c)}}( \LocalModel{M}^i  )
    |
    i = 1,\ldots,q
  }
  \text{,}
\end{equation}
which is the only model that is hence retained.

@@

\paragraph{Holdout method}
The so-called `holdout' cross-validation method ensures a good model by first splitting the dataset into two smaller disjoint datasets: e.g. $70\%$ of the data  is used to estimate the model and a goodness-of-fit criterion (e.g. cost function) is used on the remaining data to determine which model has the best out-of-sample performance.
By using independent datasets and assessing the performance of the model on (unseen) validation data, overfitted models can be rejected.

@@

\paragraph{Leave-out cross-validation}
Instead, we use a better-suited cross-validation approach known as \gls{LOOCV} that is related to the \gls{AIC}~\citep{Stone1977}.
Plainly, \gls{LOOCV} cross-validates the model by in turn leaving out each data point, estimating the local model parameters and observing the difference between the omitted data point and the estimate.
In effect, such an approach calculates the \gls{PRESS} for each local model:
\begin{equation}
 \PRESS = 
 \frac{1}{\nWind} 
  \sum_{r \in \LocalShifts{}}
    \abs{\ignoring{r}{\LocalVector{E}}}^2
    \text{,}
\label{eq:PRESS-general}
\end{equation}
where $\ignoring{r}{\LocalVector{E}} = \LocalVector{Y}_{r} - \ignoring{r}{\LocalVector{\estimated{Y}}}$, i.e. the difference between the observed (local) output spectrum at the $r^{\text{th}}$ line and the predicted output spectrum at the same line when the corresponding data point is removed from the estimation procedure.
To select the best model from a set of candidate models, only the model with the lowest \gls{PRESS} value is retained.
In general, this means that \gls{LOOCV} requires estimating $\nWind$ additional models (one for each omitted data point) and hence can be very time-consuming.

@@

\subsubsection{Combining Different Local Model Orders}
In the previous section, different methods were introduced to select the local model order.
This begs the question whether it is advantageous to use the same local model complexity over all frequencies or the model order should be kept globally.
The answer to this, depends on the ultimate purpose of the \gls{FRF}.

>>>>

\chapter{Non-parametric Modeling}
\def\thisDir{ch03-lrm}
\tikzsetfigurename{ch03fig}
\label{sec:nonparametric}
\myEpigraph{I love deadlines. I like the whooshing sound they make as they fly by.}{Douglas Adams}{}
\glsresetall

@@

\subsection{Local Model Order Selection}
\label{sec:nparam:orderSelection}
Selecting suitable values of $\nWind$, $\order{B}$, $\order{A}$ and $\order{C}$ obviously affects the quality of the obtained local models.
For local rational models, there are a few insights from parametric system identification that can be retained to make these choices easier.
In particular~\citep{Pintelon2010LPM1}:
\begin{equation}
\order{C} \leq \max\set{\order{B},\order{A}}
\end{equation}
 and from statistical point of view~\citep{Mahata2006}, the degrees of freedom should remain positive such that 
 \begin{equation}
 \nWind \geq \order{B} + \order{A} + \order{C} + 2
 \text{.}
 \end{equation}

@@

\subsubsection{Plug-in methods}
In plug-in methods, a goodness-of-fit criterion (e.g. the log-likelihood function $\LogLikelihood$ of the estimated local model $\LocalModel{M}$ given the estimation dataset $\LocalVector{Z}$), is penalized with a term accounting for the complexity of the model~\citep{Burnham2002}.
E.g. a common choice is the \gls{AIC}~\citep{Akaike1974} or the \gls{AICc}~\citep{Hurvich1989}, which are defined as
\begin{align}
\LocalVector{L}_{\AIC} &=
 - 2  \loglikelihood{\LocalModel{M} | \LocalVector{Z}} 
 + 2 \nth
\label{eq:nparam:AIC}\\
\LocalVector{L}_{\AICc} &= 
- 2  \loglikelihood{\LocalModel{M} | \LocalVector{Z}} 
+   \frac{2 \nth\nWind}{\nWind - \nth - 1}
\label{eq:nparam:AICc}
\end{align}
where $\nth$ is the number of  estimated parameters in the model $\LocalModel{M}(\theta)$.
In the context of local modeling, the \gls{AIC} is a poor choice since it relies on asymptotic arguments of the data set, i.e. $\nWind \to \infty$, which is obviously an unwarranted choice in this context.
The best model among a set of $q$ possible models $\Set{\LocalModel{M}^1, \ldots, \LocalModel{M}^q}$ is then
\begin{equation}
  \LocalModel{M}^{\star} \isdef 
  \arg\limits_{\LocalModel{M}} \min 
  \Set{
    \LocalVector{L}_{\mathrm{AIC(c)}}( \LocalModel{M}^i  )
    |
    i = 1,\ldots,q
  }
  \text{,}
\end{equation}
which is the only model that is hence retained.

@@

\subsubsection{Holdout method}
The so-called `holdout' cross-validation method ensures a good model by first splitting the dataset into two smaller disjoint datasets: e.g. $70\%$ of the data  is used to estimate the model and a goodness-of-fit criterion (e.g. cost function) is used on the remaining data to determine which model has the best out-of-sample performance.
By using independent datasets and assessing the performance of the model on (unseen) validation data, overfitted models can be rejected.

@@

\subsubsection{Leave-out cross-validation}
Instead, we use a better-suited cross-validation approach known as \gls{LOOCV}.
 that is related to the \gls{AIC}~\citep{Stone1977}.
Plainly, \gls{LOOCV} cross-validates the model by in turn leaving out each data point, estimating the local model parameters and observing the difference between the omitted data point and the estimate.
In effect, such an approach calculates the \gls{PRESS} for each local model:
\begin{equation}
 \PRESS = 
 \frac{1}{\nWind} 
  \sum_{r \in \LocalShifts{}}
  \abs{\ignoring{r}{\LocalVector{E}}}^2
    \text{,}
\label{eq:PRESS-general}
\end{equation}
where $\ignoring{r}{\LocalVector{E}} = \LocalVector{Y}_{r} - \ignoring{r}{\LocalVector{\estimated{Y}}}$, i.e. the difference between the observed (local) output spectrum at the $r^{\text{th}}$ line and the predicted output spectrum at the same line when the corresponding data point is removed from the estimation procedure.
To select the best model from a set of candidate models, only the model with the lowest \gls{PRESS} value is retained.
In general, this means that \gls{LOOCV} requires estimating $\nWind$ additional models (one for each omitted data point) and hence can be very time-consuming.

@@

\subsection{Combining Different Local Model Orders}
In the previous section, different methods were introduced to select the local model order.
This begs the question whether it is advantageous to use the same local model complexity over all frequencies or the model order should be kept globally.
The answer to this, depends on the ultimate purpose of the \gls{FRF}.

### 2016-05-08 ch05-initvals/initial-values.tex
Small stuff
Reset acronyms etc. per chapter
Some cleanup, more references input design

\chapter{Initialization of Parametric Estimators}
\label{sec:initvals}
\myEpigraph{Everything starts somewhere, though many physicists disagree. But people have always been dimly aware of the problem with the start of things. They wonder how the snowplough driver gets to work, or how the makers of dictionaries look up the spelling of words.}{Terry Pratchett}{Hogfather}
\gdef\thisDir{ch05-initvals}
\tikzsetfigurename{ch05fig}
\researchBasedOn{Geerardyn2015TIM}

\section{Introduction}
\label{sec:initial-values:introd}
The task of interpreting measurement data from dynamic systems often involves the estimation of a transfer function (TF). 
Typical measurement techniques and identification strategies of  \glspl{TF} or \glspl{FRF} are presented in~\citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF}.
Application of these methods to real devices and systems is well-represented in the literature, e.g. \citep{Lim2010,Robinson1990,Behjat2010}.

@@

  With reference to a detailed exposition in~\citep{Lumori2014TIM} and \chapref{sec:nonparametric}, the \gls{LPM} utilizes local polynomials to approximate the transfer function and transient contribution (in least squares sense) and, thus, smooth $\true{G}$ and $T$ around a central frequency $\omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$.
  In this chapter, we limit the notations to quadratic polynomials in a window with half-width $N_W=3$, such that
\begin{subequations}\label{lpmImplQuadG}
\begin{align}
\true{G}(\omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
\\
T(\omega_{k+r})&\approx T(\omega_k)+t_{1,k}r + t_{2,k}r^2
\label{lpmImplQuadT}
\end{align}
\end{subequations}
where, in general,$r \in \LocalShifts[]$ with $\LocalShifts[] = \{-N_W,-N_W+1,\dots,N_W\}$ and $N_W$ is a tunable parameter.

@@

The \gls{RFIR} estimator is formulated in the time domain. 
It estimates the impulse response of a discrete time system as the minimizer of the following regularized least squares objective function:
\begin{align}\label{eq:hRFIRdef}
\hat g_{\mathrm{RFIR}} &= \argmin_{g} \norm{y - g \ast u }^2 + \sigma^2 g^{\TT}P^{-1}g
\end{align}
where $g$ is the vectorized impulse response $g(t)$, with $t = 0,1,\cdots,n_h - 1$, assuming that the impulse response is $n_g$ samples long. 
Furthermore, $g\ast u$ is the convolution of $g$ with the input signal $u$, and $P\in \mathbb{R}^{n_g\times n_g}$ is the kernel matrix~\citep{Chen2012}. 
Note that \eqref{eq:hRFIRdef} is quadratic in $g$, such that $\hat g_{\mathrm{RFIR}}$ can be computed analytically in a single step.
The kernel matrix $P$ embodies prior knowledge on the system to be estimated. 
Here, the \gls{DCkernel}~\citep{Chen2012,Pillonetto2010} is used. 
Specifically, the element at $t_1,t_2$ of $P$ is given by
\begin{equation}
P(\alpha,\beta)_{t_1,t_2} = e^{-\alpha|t_1 - t_2|}e^{-\beta(t_1 + t_2)/2}
\end{equation}
 for $t_1,t_2 \in \left\{0,1,\cdots,n_h - 1\right\}$ which makes the estimated impulse response to be an exponentially decaying function of $t$ with decay rate $\beta^{-1}$, and correlation length $\alpha^{-1}$. 
 The latter \emph{hyperparameters} $\alpha$, $\beta$ and $\sigma$ are determined using Empirical Bayes~\citep{Carlin2000,Gelman2014}, i.e. as the maximizers of the \gls{LML} of the measured output signal~\citep{Chen2012}:
\begin{align}
\mathrm{LML}(y) = -y^{\TT}\Sigma(\alpha,\beta,\sigma)^{-1}y - \log |\Sigma(\alpha,\beta,\sigma)| \text{,}
\end{align}
where $\Sigma(\alpha,\beta, \sigma) = \sigma^2 \I + \phi^{\TT}P(\alpha,\beta)\phi$ and $\phi$ is a Toeplitz matrix constructed with $u$. 
This problem is solved using \mcode{fmincon} in \MATLAB.

@@

\begin{figure}[p]
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \centering
  \input{\thisDir/figs/distances.tikz}
  \caption[Empirical \glsentrytext{CDF} of $\validationDistance{\bullet}$ in the stress test.]{Empirical cumulative distribution function of the validation distance $D_{\bullet} = \norm{\model{\bullet} - \true{G}}$ for the different tested systems (different numbered plots) and the different initial values (colors).
  Note that since $\norm{\true{G}}=1$ is chosen, $D_{\bullet}$ immediately indicates the relative RMS error of the estimates.
  }
  \label{fig:distancesStress}
\end{figure}

@@

Overall, the time-truncated \gls{LPM} operates in $\bigO{N n_{\theta}^{3}}$.
First, the \gls{LPM} solves $\bigO{N}$ linear regression problems of small dimensions ($2N_W + 1$ data points and a few degrees of freedom, i.e. $n_{\theta} \leq 2 N_W + 1$ or $\bigO{N_W} = \bigO{n_{\theta}}$), hence the runtime will be $\bigO{N n_{\theta}^3}$ since solving a linear regression problem with $C$ parameters and $D$ data points requires $\bigO{C^3  + D C^2}$ operations\footnote{See \url{http://math.stackexchange.com/questions/84495}}.
The truncation of the impulse response relies on linear regression which takes $\bigO{N}$ operations since only $3$ parameters are estimated during this step.
As such, carrying out the first $\bigO{N n_{\theta}^3}$ step and then the $\bigO{N}$ step, the whole procedure remains a $\bigO{N n_{\theta}^3}$ or, equivalently, $\bigO{N N_W^3}$.

@@

The computational complexity  of both methods scales linearly in the length of the dataset.
However, since the required length $n_g$ of a \gls{FIR} filter is typically a lot more (e.g. $200$ in this chapter) than the number of local parameters (or bandwidth) of the \gls{LPM} (e.g. $N_W = 3$), it can be seen that eventually the \gls{RFIR} method will scale less favorably for the model complexity of the smoother.
Intuitively, the local modeling methods benefit from their locality since that enables them to be flexible without a huge amount of parameters.

>>>>

\chapter{Initialization of Parametric Estimators}
\label{sec:initvals}
\myEpigraph{Everything starts somewhere, though many physicists disagree. But people have always been dimly aware of the problem with the start of things. They wonder how the snowplough driver gets to work, or how the makers of dictionaries look up the spelling of words.}{Terry Pratchett}{Hogfather}
\gdef\thisDir{ch05-initvals}
\tikzsetfigurename{ch05fig}
\glsresetall
\researchBasedOn{Geerardyn2015TIM}

\section{Introduction}
\label{sec:initial-values:introd}
The task of interpreting measurement data from dynamic systems often involves the estimation of a \gls{TF}. 
Typical measurement techniques and identification strategies of  \glspl{TF} or \glspl{FRF} are presented in~\citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF}.
Application of these methods to real devices and systems is well-represented in the literature, e.g. \citep{Lim2010,Robinson1990,Behjat2010}.

@@

  With reference to a detailed exposition in~\citep{Lumori2014TIM} and \chapref{sec:nonparametric}, the \gls{LPM} utilizes local polynomials to approximate the transfer function and transient contribution (in least squares sense) and, thus, smooth $\true{G}$ and $T$ around a central frequency $\omega_{k}$ in a local frequency band $\omega_{k+r}\in\LocalWindow$.
  In this chapter, we limit the notations to quadratic polynomials in a window with half-width $\numel{W}=3$, such that
\begin{subequations}\label{lpmImplQuadG}
\begin{align}
\true{G}(\omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
\\
T(\omega_{k+r})&\approx T(\omega_k)+t_{1,k}r + t_{2,k}r^2
\label{lpmImplQuadT}
\end{align}
\end{subequations}
where $r \in \LocalShifts{k}$ with $\LocalShifts{k} = \{-\numel{W},-\numel{W}+1,\dots,\numel{W}\}$ and $\numel{W}$ is a tunable parameter.

@@

The \gls{RFIR} estimator is formulated in the time domain. 
It estimates the impulse response of a discrete time system as the minimizer of the following regularized least squares objective function:
\begin{align}\label{eq:hRFIRdef}
\hat g_{\mathrm{RFIR}} &= \argmin_{g} \norm{y - g \conv u }^2 + \sigma^2 g^{\TT}P^{-1}g
\end{align}
where $g$ is the vectorized impulse response $g(t)$, with $t = 0,1,\cdots,n_h - 1$, assuming that the impulse response is $n_g$ samples long. 
Furthermore, $g\conv u$ is the convolution of $g$ with the input signal $u$, and $P\in \mathbb{R}^{n_g\times n_g}$ is the kernel matrix~\citep{Chen2012}. 
Note that \eqref{eq:hRFIRdef} is quadratic in $g$, such that $\hat g_{\mathrm{RFIR}}$ can be computed analytically in a single step.
The kernel matrix $P$ embodies prior knowledge on the system to be estimated. 
Here, the \gls{DCkernel}~\citep{Chen2012,Pillonetto2010} is used. 
Specifically, the element at $t_1,t_2$ of $P$ is given by
\begin{equation}
P(\alpha,\beta)_{t_1,t_2} = e^{-\alpha|t_1 - t_2|}e^{-\beta(t_1 + t_2)/2}
\end{equation}
 for $t_1,t_2 \in \left\{0,1,\cdots,n_h - 1\right\}$ which makes the estimated impulse response to be an exponentially decaying function of $t$ with decay rate $\beta^{-1}$, and correlation length $\alpha^{-1}$. 
 The latter \emph{hyperparameters} $\alpha$, $\beta$ and $\sigma$ are determined using Empirical Bayes~\citep{Carlin2000,Gelman2014}, i.e. as the maximizers of the \gls{LML} of the measured output signal~\citep{Chen2012}:
\begin{align}
\mathrm{LML}(y) = -y^{\TT}\Sigma(\alpha,\beta,\sigma)^{-1}y - \log |\Sigma(\alpha,\beta,\sigma)| \text{,}
\end{align}
where $\Sigma(\alpha,\beta, \sigma) = \sigma^2 \I + \phi^{\TT}P(\alpha,\beta)\phi$ and $\phi$ is a Toeplitz matrix constructed with $u$. 
This problem is solved using \mcode{fmincon} in \MATLAB.

@@

\begin{figure}[p]
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \centering
  \input{\thisDir/figs/distances.tikz}
  \caption[Empirical \glsentrytext{CDF} of $\validationDistance{\bullet}$ in the stress test.]{Empirical cumulative distribution function of the validation distance $D_{\bullet} = \norm[2]{\model{\bullet} - \true{G}}$ for the different tested systems (different numbered plots) and the different initial values (colors).
  Note that since $\norm[2]{\true{G}}=1$ is chosen, $D_{\bullet}$ immediately indicates the relative RMS error of the estimates.
  }
  \label{fig:distancesStress}
\end{figure}

@@

Overall, the time-truncated \gls{LPM} operates in $\bigO{N n_{\theta}^{3}}$.
First, the \gls{LPM} solves $\bigO{N}$ linear regression problems of small dimensions ($2\numel{W} + 1$ data points and a few degrees of freedom, i.e. $n_{\theta} \leq 2 \numel{W} + 1$ or $\bigO{\numel{W}} = \bigO{n_{\theta}}$), hence the runtime will be $\bigO{N n_{\theta}^3}$ since solving a linear regression problem with $C$ parameters and $D$ data points requires $\bigO{C^3  + D C^2}$ operations\footnote{See \url{http://math.stackexchange.com/questions/84495}}.
The truncation of the impulse response relies on linear regression which takes $\bigO{N}$ operations since only $3$ parameters are estimated during this step.
As such, carrying out the first $\bigO{N n_{\theta}^3}$ step and then the $\bigO{N}$ step, the whole procedure remains a $\bigO{N n_{\theta}^3}$ or, equivalently, $\bigO{N \numel{W}^3}$.

@@

The computational complexity  of both methods scales linearly in the length of the dataset.
However, since the required length $n_g$ of a \gls{FIR} filter is typically a lot more (e.g. $200$ in this chapter) than the number of local parameters (or bandwidth) of the \gls{LPM} (e.g. $\numel{W} = 3$), it can be seen that eventually the \gls{RFIR} method will scale less favorably for the model complexity of the smoother.
Intuitively, the local modeling methods benefit from their locality since that enables them to be flexible without a huge amount of parameters.
